Meeting Notes---Summary LLM

### 2024-03-12 meetings/meeting_notes.qmd
notes SURF workshop

>>>>

# 12-03-2024 ([Surf Research Cloud Workshop](https://www.surf.nl/en/agenda/introduction-to-surf-research-cloud-11))

- [Available flavors](https://servicedesk.surf.nl/wiki/display/WIKI/SRC+Available+Flavours)
- [Small Compute Applications (E-Infra grant)](https://www.surf.nl/en/small-compute-applications-nwo)
  - [documentation](https://servicedesk.surf.nl/wiki/display/WIKI/Paying+for+usage)
  - 1 year valid, can apply every *calendar* year
  - up to 5,000 GPU hours
  - can extend by 6 months if resources are left
  - goes through SURF, can help with resources
  - Estimate by iteration time, core hours + 20% overhead
  - Need somebody who has permanent contract with Dutch institution
  - hard *not* to get
- NWO Groot grant is bigger, but slower and harder to get
  - Can chain this together with the small compute applications
- At EUR will create new policy on this next month
- Sounds like there will be resources that your department can free up directly
- RCCS contract
- Likly much faster GPUs then e.g. Google Colab
- Can also have budgets at other Cloud services and use research cloud for collaboration, e.g. Azure, AWS
- Could we get resources for the NLP course? They are also dedicated to education, not only research

## People

- Pieter Meijndert, ESE, Head of Business Intelligence and Application Management
- Yuliia Orlova, Liasion User-Developers
- Carsten Schelp

## Workshop

- Pick collaboration and budget work a workspace, people from collaboration get access
- e.g RStudio, Jupyter available
- Disk budget will expire when grant expires, not an archive. Quite fast discs. Only upload data once and use from multiple instances.
- Storage is persistent, data is not lost if VM crashes.
- Attach the storage to the workspace
- Set deadline for the machine, normal lifetime is 5 days
- Shortlifed instances support reproduceability
- RStudio "username": Profile tab of the portal; time-based password. For Jupyter its the portal credentials.
  - Can also be SSH for some instances
- Can probably connect through VSCode and SSH to instance directly
- Whisper instance on cloud, useful for transcription?

## Questions

- What is a GPU core hour?
